Assessment of the KLGO Coastal Waterbird Survey Monitoring Program

### 2019-02-09 analysis/paper/paper.Rmd
Separated functionality in 'data_exploration.R' into a 'data_wrangling' script and a 'survey_timing' data visualization script. Modified 'data_retrievalCSV' to suppress messages. Modifications to r code chunks to get knitr to compile to html, word, or pdf.

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  fig.path = "../figures/"
)

library(dplyr);library(ggplot2);library(dbplyr);library(readr);library(stringr);library(tidyr);library(lubridate);library(ggthemes);library(ggforce)

```
# Things To Discuss
- add all libraries used in scripts to 'setup' code chunk (just above) rather than just loading in script so that it is easy to see what needs to be loaded before you can successfully knit.

@@

```{r DataInput, eval=TRUE, echo=FALSE, cache=TRUE}
# if (system("git config user.email")=="mward2@swarthmore.edu") 
#      source("./scripts/data_retrievalSwarthmore.R")
# else source("./scripts/data_retrievalNPS.R")

@@

@@

```{r, eval=TRUE}
source("../scripts/data_exploration.R") 
```

>>>>

```{r setup, include=FALSE, cache = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = TRUE, # set to FALSE when done
  message = TRUE, # set to FALSE when doen
  echo = FALSE,
  comment = "#>",
  dev = c('png','pdf'),
  pdf.options(encoding = "ISOLatin9.enc"),
  fig.path = "../figures/",
  error = FALSE
)

library(dplyr);library(ggplot2);library(dbplyr);library(readr);library(stringr);library(tidyr);library(lubridate);library(lattice);library(ggthemes);library(ggforce)

```
# Things To Discuss with Madeleine
- add all libraries used in scripts to 'setup' code chunk (just above) rather than just loading in script so that it is easy to see what needs to be loaded before you can successfully knit.
- documentation in scripts

# Issues to Resolve
- why isn't code chunk option warning= FALSE suppressing warnings() in Data_Retrieval? (from read_csv)
- How do we use latex figure environment in rmarkdown (for inclusion of ggplot graphics; captioning figures and labelling for cross-references, etc)?
- conversion from paper.md to paper.pdf (pandoc issue?) (i) update MikTex package, set dev=c('pdf') in setup
- github permissions for Madeleine on local machine
- What is up with 2008 surveys? why such distinct timing?

@@

```{r Data_Retrieval, eval=TRUE, echo=FALSE, warning = FALSE}
# if (system("git config user.email")=="mward2@swarthmore.edu") 
#      source("./scripts/data_retrievalSwarthmore.R")
# else source("./scripts/data_retrievalNPS.R")

@@

```{r Data_Wrangling, eval=TRUE, echo=FALSE, warning = TRUE}
# reconstructs species_data tibble from tables read in by DataInput
#
source("../scripts/data_wrangling.R")

@@

```{r EDA_SurveyTiming, eval=TRUE, cache = FALSE, fig.show= 'asis'}
 source("../scripts/survey_timing_EDA.R", echo=FALSE) 
print(Plot1)
